\begin{thebibliography}{99}

\bibitem {1} \emph{El lenguaje unificado de modelado.} \\
Booch G., Rumbaugh J., Jacobson I. \\ Addison-Wesley Pub. Co , 1999.

\bibitem {2} \emph{Junit framework.} \\ http://www.junit.org

\bibitem {3} \emph{MySQL Home Page.} \\ http://www.mysql.com

\bibitem {4} \emph{Selenium Project.} \\ http://seleniumhq.org

\bibitem {5} \emph{What is Web 2.0} \\ O’ Reilly T. \\ http://www.oreilly.com

\bibitem {6} \emph{Magic Draw Home Page.} \\ http://www.magicdraw.com

\bibitem {7} \emph{CSS Home Page.} \\ http://www.w3.org/Style/CSS

\bibitem {8} \emph{Aplicaciones JavaScript.} \\ Bradenbaugh J. \\ Anaya. 2000

\bibitem {9} \emph{JavaScript. The definitive guide.} \\ Flanagan D. \\ O’Really. 2002

\bibitem {10} \emph{Utilizacion de UML.} \\ Stevens P,, Pooley R. \\ Addison Wesley. 2002.

\bibitem {11} \emph{Comparativa de frameworks web.} \\ Degiovannini M. \\ http://www.javahispano.org/

\bibitem {12} \emph{Página web de Integración de Sistemas.} \\ http://www.tic.udc.es/is-java/

\bibitem {13} \emph{Wikipedia.} \\ http://www.wikipedia.org.

\bibitem {14} \emph{Spring Framework.} \\ http://www.springframework.org.

\bibitem {15} \emph{Craig Walls with Ryan Breidenbach. Spring in action.} \\
Manning, cop. \\ 2nd. edition, 2008.

\bibitem {16} \emph{Expert One-on-One J2EE Design & Development.} \\ Rod Johnson. \\
Wrox Press Ltd., Birmingham, UK, UK, 2002.

\bibitem {17} \emph{Hibernate.} \\ http://www.hibernate.org.

\bibitem {18} \emph{Tapestry.} \\ http://tapestry.apache.org.

\bibitem {19} \emph{Java persistence with Hibernate.} \\ Christian Bauer and Gavin King. \\
Manning, 2007, rev. edition, 2007.

\bibitem {20} \emph{Tapestry in Action.} \\ Howard M. Lewis Ship. \\
Manning Publications Co., Greenwich, CT, USA, 2004.

\bibitem {21} \emph{Tapestry 5 : building web applications.} \\ Alexander Kolesnikov. \\
Birmingham : Packt, 2008, 2008.

\bibitem {22} \emph{Apache Maven Project.} \\ http://maven.apache.org.

\bibitem {23} \emph{Apache Ant Project.} \\ http://ant.apache.org.

\bibitem {24} \emph{Eclipse.} \\ http://www.eclipse.org.

\bibitem {25} \emph{Subversion.} \\ http://subversion.tigris.org.

\bibitem {26} \emph{Introducción a la edición de documentos con LATEX.} \\
Laura M. Souto. \\ http://madsgroup.org/sta/laura/latex.

\bibitem {27} \emph{Core J2EE Patterns: Best Practices and Design.} \\
Deepak Alur, John Crupi, and Dan Malks. \\
Prentice Hall PTR, 2nd edition, 2003.

\bibitem {28} \emph{Core j2ee patterns.} \\ Sun Microsystems Inc. \\
http://java.sun.com/blueprints/corej2eepatterns.

\bibitem {29} \emph{Apache Tomcat.} \\ http://tomcat.apache.org.

\bibitem {30} \emph{The Apache Software Foundation.}
Apache JMeter
http://jakarta.apache.org/jmeter/

\bibitem {31} \emph{Google.} \\ http://www.google.es.

\bibitem {32} \emph{JW FLV Media Player.} \\ http://www.longtailvideo.com/players/jw-flv-player/

\bibitem {33} \emph{Java Code Conventions, September 1997.} \\
http://java.sun.com/docs/codeconv/CodeConventions.pdf.

\bibitem {34} \emph{Tapestry Tutorial.} \\ Howard Lewis Ship. \\
The Apache Software Foundation, 2003.

\bibitem {35} \emph{Jakarta tapestry.} \\ Rob Smith. \\ 2004.

\bibitem {36} \emph{FFMpeg.} \\ http://ffmpeg.org

\bibitem {37} \emph{CubicTest IDE.} \\ http://boss.bekk.no/cubictest/index.html

\bibitem {38} \emph{iBatis.} \\ http://ibatis.apache.org/

\bibitem {39} \emph{PostgreSQL} \\ http://www.postgresql.org/

\bibitem {40} \emph{Microsoft Project} \\ http://office.microsoft.com/project


\end{thebibliography}


